Between Subgraph Isomorphism and Maximum Common Subgraph

### 2016-09-01 paper/paper.tex
complement graphs section, nds corollary + sketch proof

If defined similarly, a maximum common non-induced subgraph would allow us to select every vertex in
the smaller of the two graphs, and none of the edges. It is therefore traditional to change the
objective to maximise the number of edges selected, rather than vertices, when a non-induced common
subgraph is sought---this problem is usually called the maximum common \emph{partial} subgraph
problem instead. However, this is not what we will be discussing in this paper: maximum common
subgraph problems are symmetric in their inputs, but when discussing the non-induced case we are
allowing extra edges only in the target graph, not in the pattern.
\todo{is this example graph still needed??}
\subsection{Constraint Models and Algorithms}

@@

@@

Let $S = ( s_1 , \ldots , s_n )$ and $T = ( t_1 , \ldots , t_m)$ be two sequences.  We say that $S
\preceq T$ if $n \leq m$ and $\forall s_i \in S$ there exists a distinct $t_j \in T$ with $s_i \leq
t_j$.  (When considering a $k$-less-subgraph isomorphism) we say that $S \lesspreceq{k}
T$ if $n - k \leq m$ and $\forall s_i \in S \setminus S_k$, where $S_k$ is a subsequence of $S$
containing up to $k$ members of $S$, there exists a distinct $t_j \in T$ with $s_i - k \leq t_j$.

\begin{proposition}
If $p \lessmap{k} t$, then $\nds(p) \lesspreceq{k} \nds(t)$.
\end{proposition}

\begin{proof}
Let $p \lessmap{k} t$.  Then $\deg(p) - k \leq \deg(q)$, by Proposition 1, which
implies that $|\nds(p)| -k \leq |\nds(t)|$.

Also, $p \lessmap{k} t$ implies that for each $q \in N(p)\setminus P_k$, where $P_k$
is some subset of $P$ with $|P_k| \leq k$, $q \lessmap{k} u$, where $u \in N(t)$ and
each $u$ is distinct.  Then $\deg(q) - k \leq \deg(u)$, by Proposition 1.  Hence $\nds(p)
\lesspreceq{k} \nds(t)$.
\end{proof}

@@

\begin{corollary}
You can just ignore the first K things in $\nds(p)$, assuming it's ordered.
\end{corollary}

\begin{proof}
Do we need this?
\end{proof}

\begin{figure}
    \begin{center}
        \begin{tikzpicture}[every node/.style={circle, inner sep=1mm}]
            \node[fill=black] (p) {};
            \node[draw=none,right of = p,node distance=3mm,yshift=-1mm] {$p$};
            \node[fill=uofglawn] (n2) [above of = p,node distance=12mm] {};
            \node[fill=uofgpumpkin] (n1) [left of = n2] {};
            \node[fill=uofglawn] (n3) [right of = n2] {};
            \node[fill=uofgcobalt] (q) [above of = n2,node distance=12mm] {};
            \path (p) edge (n1) edge (n2) edge (n3)
                (n1) edge (q)
                (n2) edge (n3) edge (q)
                (n3) edge (q);
        \end{tikzpicture}
        \caption{Graph that Craig wanted}
        \label{fig:nds}
    \end{center}
\end{figure}

@@

We're not going to thank anyone, no, no.

>>>>

If defined similarly, a maximum common non-induced subgraph would allow us to select every vertex in
the smaller of the two graphs, and none of the edges. It is therefore traditional to change the
objective to maximise the number of edges selected, rather than vertices, when a non-induced common
subgraph is sought---this problem is usually called the maximum common \emph{partial} subgraph
problem instead. However, this is not what we will be discussing in this paper: maximum common
subgraph problems are symmetric in their inputs, but when discussing the non-induced case we are
allowing extra edges only in the target graph, not in the pattern.

\todo{is this example graph still needed?? yes, Patrick likes pictures}

\subsection{Constraint Models and Algorithms}

@@

\section{Relationship between non-induced and induced subgraph isomorphism}

The \emph{complement} of a graph $P$ is the graph $\bar{P}~$.  Adjacent vertices in $P$ are non-adjacent in $\bar{P}$ while non-adjacent vertices in $P$ are adjacent in $\bar{P}$.

\begin{proposition}\label{prop:comp}
Let $i$ be an assignment of $T$ vertices to $P$ vertices.  Then $i$ satisfies the definition of $P \hookrightarrow T$ if and only if both $i$ satisfies the definition of $P \rightarrowtail T$ and $\bar{P} \rightarrowtail \bar{T}$.
\end{proposition}

\begin{proof}
Follows directly from the definition of an induced subgraph isomorphism and the definition of the complement of a graph.  Could flesh this out if we need to fill up space and look cleverer??
\end{proof}

\begin{corollary}
Let $i$ be an assignment of $T$ vertices to $P$ vertices.  Then $i$ satisfies the definition of $P \lessind{k} T$ if and only if both $i$ satisfies the definition of $P \lessnonind{k} T$ and $\bar{P} \lessnonind{k} \bar{T}$.
\end{corollary}

Should we just give the corollary as the proof??

In our algorithm we make use of \cref{prop:comp} by seeking an $i$ which simultaneously satisfies $P \rightarrowtail T$ and $\bar{P} \rightarrowtail \bar{T}$ when searching for an induced subgraph isomorphism.  Further, \cref{prop:comp} tells us that every induced subgraph isomorphism is equivalent to simultaneous non-induced subgraph isomorphisms both $P$ and $T$ as well as their complements.

@@

Let $S = ( s_1 , \ldots , s_n )$ and $T = ( t_1 , \ldots , t_m)$ be two sequences.  We say that $S
\preceq T$ if $n \leq m$ and $\forall s_i \in S$ there exists a distinct $t_j \in T$ with $s_i \leq
t_j$.  When considering a $k$-less-subgraph isomorphism we say that $S \lesspreceq{k}
T$ if $n - k \leq m$ and $\forall s_i \in S \setminus S_k$, where $S_k$ is a subsequence of $S$
containing up to $k$ members of $S$, there exists a distinct $t_j \in T$ with $s_i - k \leq t_j$.

\begin{proposition}\label{prop:nds}
If $p \lessmap{k} t$, then $\nds(p) \lesspreceq{k} \nds(t)$.
\end{proposition}

\begin{proof}
Let $p \lessmap{k} t$.  Then $\deg(p) - k \leq \deg(q)$, by \cref{prop:deg}, which
implies that $|\nds(p)| -k \leq |\nds(t)|$.

Also, $p \lessmap{k} t$ implies that for each $q \in N(p)\setminus P_k$, where $P_k$
is some subset of $P$ with $|P_k| \leq k$, $q \lessmap{k} u$, where $u \in N(t)$ and
each $u$ is distinct.  Then $\deg(q) - k \leq \deg(u)$, by \cref{prop:deg}.  Hence $\nds(p)
\lesspreceq{k} \nds(t)$.
\end{proof}

@@

\begin{corollary}
Since both $\nds(p)$ and $\nds(t)$ are non-ascending, wlog we can replace $S \setminus S_k$ from the definition of $S \lesspreceq{k}
T$ with $S[k, n]$.
\end{corollary}

\begin{proof}
Sketch?? Let $S_k$ be some elements of the sequence which aren't the first $k$ elements.  Then these elements are less than or equal to the first $k$ elements.
\end{proof}

\begin{figure}
    \begin{center}
        \begin{tikzpicture}[every node/.style={circle, inner sep=1mm}]
            \node[fill=black] (p) {};
            \node[draw=none,right of = p,node distance=3mm,yshift=-1mm] {$p$};
            \node[fill=uofglawn] (n2) [above of = p,node distance=12mm] {};
            \node[fill=uofgpumpkin] (n1) [left of = n2] {};
            \node[fill=uofglawn] (n3) [right of = n2] {};
            \node[fill=uofgcobalt] (q) [above of = n2,node distance=12mm] {};
            \path (p) edge (n1) edge (n2) edge (n3)
                (n1) edge (q)
                (n2) edge (n3) edge (q)
                (n3) edge (q);
        \end{tikzpicture}
        \caption{Example of neighbourhood degree filtering cases}
        \label{fig:nds}
    \end{center}
\end{figure}

@@

We're not going to thank anyone, no, no.  Thanks to Frances for making us less smelly throughout the writing of the paper (by thieving toiletries from a fancy hotel).
